The Astropy Project: \\ Sustaining and Growing a Community-oriented Open-source Project and the Latest Major Release (v5.0) of the Core Package

### 2022-03-09 src/ms.tex
fix figures build

% To allow putting figures in a subdir
\graphicspath{{figures/}}

@@

\begin{figure}
    \begin{centering}
      \includegraphics{figures/commits_committers_per_month.pdf}
        \caption{
            \todo{Adrian}{Write caption@}
        }
        \label{fig:contributor-summary:commits_committers_per_month}
    \end{centering}
\end{figure}

\begin{figure*}
    \begin{centering}
      \includegraphics{figures/Ncommitters_vs_frac_commits.pdf}
        \caption{
            \todo{Adrian}{Write caption@}
        }
        \label{fig:contributor-summary:Ncommitters_vs_frac_commits}
    \end{centering}
\end{figure*}

\begin{figure*}
    \begin{centering}
      \includegraphics{figures/top_contributors_career.pdf}
        \caption{
            \todo{Adrian}{Write caption@}
        }
        \label{fig:contributor-summary:top_contributors_career}
    \end{centering}
\end{figure*}

>>>>

% To allow putting figures in a subdir
% \graphicspath{{figures/}}

@@

\begin{figure}
    \begin{centering}
      \includegraphics[width=0.5\textwidth]{commits_committers_per_month.pdf}
        \caption{
            todo
        }
        \label{fig:contributor-summary:per-month}
    \end{centering}
\end{figure}

\begin{figure}
    \begin{centering}
      \includegraphics[width=\textwidth]{Ncommitters_vs_frac_commits.pdf}
        \caption{
            todo
        }
        \label{fig:contributor-summary:Ncommitters}
    \end{centering}
\end{figure}

\begin{figure}
    \begin{centering}
      \includegraphics[width=0.75\textwidth]{top_contributors_career.pdf}
        \caption{
            todo
        }
        \label{fig:contributor-summary:top}
    \end{centering}
\end{figure}
